Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-16 RR_manuscript/Draft_RR.Rmd
♻️ - add reason for team dropping

`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate in the study.
<!-- TODO: Add reasons for dropping out -->
`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the signed-up teams dropped out during the analysis phase^[ADD REASONS]. 
The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis by the established deadline.
These are the teams that are included in this study.

>>>>

`r team_desc_list$Initial$n_teams$val %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate in the study.
<!-- TODO: Add reasons for dropping out -->
`r (team_desc_list$Initial$n_teams$val - team_desc_list$Final$n_teams$val) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the signed-up teams dropped out during the analysis phase.
One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: "The reason is that [...] the project's approach is too much top-down instead of bottom-up. [...] I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data."
We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to asnwer one research question.
The remaining `r team_desc_list$Final$n_teams$val` teams submitted their analysis by the established deadline.
These are the teams that are included in this study.

### 2022-09-16 RR_manuscript/Draft_RR.tex
♻️ - add reason for team dropping

Eighty-Four teams initially signed up to participate in the study.
Fifty-Four of the signed-up teams dropped out during the analysis phase\footnote{ADD REASONS}.
The remaining 30 teams submitted their analysis by the established deadline.
These are the teams that are included in this study.

@@

45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 5\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
For example,

@@

As explained in the \textbf{Methods} section, the primary aim of this is to assess the variability of the reported effects or, in other words, the degree of between-team variability.
As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team returned by the meta-analytic model.

@@

\textbf{Non-preregistered}. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
We have run two further non-preregistered meta-analytic models:

@@

On the one hand, the second non-preregistered model reveals that the posterior estimate for model ID is identical to that of the first non-preregistered model.
On the other hand, the posterior 95\% CrI for team in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.

@@

We gave XX analyst teams the same speech dataset to answer the same research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}.
In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct an appropriate statistical model to answer the research question.
As shown by the results of this meta-analytic study, such complex process has led to a wide ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
Every individual analyst team has chosen unique paths to acoustically measure, operationalize and statistical analyse the data.
Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
The variation in reported effect sizes was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams.
Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience \citep[e.g.,][\citet{breznau2021observing}]{silberzahn2018many}.
Given the mounting evidence, \citet{breznau2021observing} conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions.''
Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.

While properties of the teams did not seem to systematically affect results, teams' estimates seem to depend on certain measurement choices.
Human speech is a complex multidimensional signal.
Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in.
Some outcome choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another.
For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
This asymmetry can have several causes.
First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to strong biases.
Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
Third, ADD REASONS.
Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.

It particularly struck us that teams did not follow our instructions to only submit a single effect size.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for \citep[Tukey 1953,][]{benjamini1995controlling}.
It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking} while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.

@@

The current results point to important barriers for successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature {[}e.g., REFERENCE{]}.
One of the suggested paths forward is for researchers to directly replicate previous study more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
The quantitative sciences are in an inference crisis \citep{rotello2015more, starns2019assessing}.
Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, they also seemed to consider all these alternative approaches acceptable, as their peer-ratings suggest.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.

A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to entirely different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated with much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
Without well defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.

In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility (LeBel et al., 2018).
It allows for alternative analyses to establish analytic robustness (Steegen et al., 2016) and strengthens attempts to synthesize evidence via meta-analyses (Nicenboim et al., 2018)
This enables critical evaluation and robustness checks by other fellow researchers (REF).
Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process {[}e.g., CITE Praat, EMU CITE){]}{]}.

ADD

@@

Third, if researchers have a good understanding of relevant analytic degrees of freedom, they could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
This approach is called ``multiverse analysis'' \citep[e.g,][]{steegen2016increasing, harder2020multiverse} and has recently gained popularity across disciplines.
Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored.
Crowd-sourcing is limited by the sampled analysts and their biases.
Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
Eventually, a mature scientific discipline should develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal.
This can be achieved by formalizing verbal expectations mathematically or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.

@@

Our study has several limitations that need to be considered when evaluating our results.
First, there is potential for bias. The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods. We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field.
This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom.
We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices detectable.
However, our results should be independently re-analysed and replicated using a different research question.
Moreover, our sample is an opportunity sample.
We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
Moreover, while the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate meta-analytic estimates reliably.
This is particularly important for the predictor evaluation.
Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty.
This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects \citep{auspurg2021has}.
However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see \citet{scheel2022most}) a common phenomenon.
For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.
- We have not investigated researcher positionality, which is known to be an important factor.

Despite these possible sources of uncertainty and bias, our study suggest that at a minimum we can expect the between-team variability that we have observed, which is quite substantial and possibly amplifying biases.

Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
Our focus was on quantitative analyses that require operationalization of a multidimensional signal. While some of our results can be informative for other disciplines working with speech or video signals, they are not very informative for expected variation between analysts working in qualitative fields of research.
This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods. It is conceivable that the issues raised here to apply differently or not at all to qualitative data analysis.

>>>>

Eighty-Four teams initially signed up to participate in the study.
Fifty-Four of the signed-up teams dropped out during the analysis phase.
One Team Coordinator, Wim van Dommelen (who agreed to their feedback being shared), gave the following reason: ``The reason is that {[}\ldots{]} the project's approach is too much top-down instead of bottom-up. {[}\ldots{]} I would rather prefer to explore the collected utterances and run different types of acoustic analyses, which would then be followed by statistical evaluation of the data.''
We find this contribution to clearly speak to the main objective of the current study: investigate researcher's degrees of freedom in the speech sciences.
Based on our personal experience with research in the field, it is common practice to test as many different types of models, using as many different types of measurements, to asnwer one research question.
The remaining 30 teams submitted their analysis by the established deadline.
These are the teams that are included in this study.

@@

45\% of models obtained acoustic measures at the level of the segment (e.g.~comparing the acoustic profile of a vowel), 44\% from the word level (e.g.~comparing the acoustic profile of \emph{Banane} `banana'), 4\% at the level of the phrase (e.g.~the noun phrase including determiner and adjective, e.g.~``the green banana''), 2\% from the whole sentence, and 5\% used a different time window.
Based on a coarse coding of how acoustic measures were operationalized, we find a total of 52 different measurement specifications.
For example, if we look at those analyses who targeted fundamental frequency (f0), it was operationalized in a myriad of ways including as the minimum, the maximum, the mean, the median, as a range in an interval or a ratio between two intervals.
The measurement was taken from the interval of a vowel in the article, the adjective or noun, or in the word interval of article, adjective or noun, or the noun phrase interval or the entire phrase.
Some of these measures were normalized relative to other elements in the sentence or relative to the speaker.

@@

As explained in the \textbf{Methods} section, the primary aim of this analysis is to assess the degree of between-team variability.
As a measure of between-team variability, we chose to use the meta-analytic group-level standard deviation \(\sigma_{\alpha_{\text{t}}}\)), i.e.~the standard deviation of the group-level effect of team returned by the meta-analytic model.

@@

\textbf{Non-preregistered}. In our preregistration we did not take into account the possibility that teams might submit multiple analyses/models.
We have run two further non-preregistered meta-analytic models to account for this added hierarchical layer:

@@

The second non-preregistered model yields a similar model ID estimate to that of the first non-preregistered model.
However, the posterior 95\% CrI for between-team variability in the second non-preregistered model is 0 and 0.05 standard units (\(\beta\) = 0.02, SD = 0.01), corresponding to a mean deviation range of ±0.1 standard units.
One interpretation of these estimates is that the variability of effects is larger within teams than it is across teams.

@@

We gave 30 analyst teams the same speech dataset to answer the same research question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}.
In order to answer this question, teams had to operationalize latent variables within a multidimensional signal, operationalize and chose appropriate predictors, and construct appropriate statistical models to answer the research question.
This complex process has led to a vast ``garden of forking paths'', i.e.~to a wide range of combinations of possible analytical decisions.
Analyses exhibited at least 45 unique ways of operationalizing the acoustic signal alongside 52 unique ways of constructing their statistical model, amounting to 2340 possible unique combinations.
This is just a bare minimum estimate for the vast multiverse of analytical decisions, ignoring for example detailed ways of extracting the chosen acoustic parameters.

Interestingly, the observed variation in reported effect sizes was not predicted by the analysts' prior expectations about the phenomenon.
In fact, teams on average rated the plausibility of the effect as rather high before receiving access to the data.
The observed variation was neither predicted by the analysts' experience in the field nor by the perceived quality of the analysis as judged by other teams.
Analyses received overall high peer ratings for both the acoustic and the statistical analysis, suggesting that reviewers were generally satisfied with the other teams' approaches.
These findings are very much in line with previous crowd-sourced projects that suggest variation between teams is neither driven by perceived quality of the analysis nor by analysts biases or experience \citep[e.g.,][\citet{breznau2021observing}]{silberzahn2018many}.
Given the mounting evidence, \citet{breznau2021observing} conclude that ``{[}\ldots{]} we are left to believe that idiosyncratic uncertainty is a fundamental feature of the scientific process that is not easily explained by typically observed researcher characteristics or analytic decisions.''
Idiosyncratic variation across researchers might be a fact of life which researchers have to acknowledge and integrate into how they evaluate and present evidence.

While properties of the teams did not seem to systematically affect results, teams' estimates seem to depend on certain measurement choices.
Human speech is a complex multidimensional signal.
Researchers need to make choices about what to measure, how to measure it and which temporal unit to measure it in.
Some outcome choices seem to bias the estimates in our data in one direction while others seem to bias estimates into another.
For example, measurements related to fundamental frequency tended to result in lower estimates while measurements related to vowel formants tended to yield higher estimates.
This asymmetry can have several causes.
First, there could be a true underlying relationship between typicality and the speech signal that manifests itself in some measures but not others and/or manifests itself negatively in one acoustic measure but positively in another.
Second, certain measurement choices might be associated with stronger expectations relative to the research question, which might lead to stronger biases.
Many researchers targeted measures related to voice fundamental frequency (f0) since similar functional relationships like information structure and predictability can be expressed via f0 \citep[e.g.][]{grice2017integrating, turnbull2017role}.
Regardless of its cause, we have to conclude that depending on the choice of how the speech signal is operationalized, researchers might find evidence for or against a theoretically relevant effect.

It particularly struck us that most teams submitted many different models.
Teams submitted up to 16 different models to test for a possible relationship between typicality and the speech signal.
Obviously, the complexity of the speech signal lends itself to multiple approaches, but this plurality of hypothesis tests invites bias and can dramatically increase the rate of falsely claiming the presence of an effect \citep{roettger2019researcher}.
When operating within the frequentist inferential framework, testing the same hypothesis with different dependent variables, increases the Type-I error rate if not corrected for \citep[Tukey 1953,][]{benjamini1995controlling}.
It also invites bias, possibly leading to the selective reporting of those tests that yield a desirable outcome \citep[\citet{john2012measuring}, \citet{simmons2011false}]{kerr1998harking} while null results remain unreported \citep[e.g.,][\citet{rosenthal1979file}]{sterling1959publication}.
Fields such as the speech sciences who generate knowledge based on multidimensional data, should be aware of this flexibility and calibrate their confidence in empirical claims accordingly.

@@

The current results point to important barriers for successful accumulation of knowledge.
The replication crisis has brought attention to scientific practices that lead to unreliable and biased claims in the literature \citep[e.g.,][\citet{fidler2018reproducibility}]{vazire2017quality}.
One of the suggested paths forward is for researchers to directly replicate previous study more often \citep[e.g.,][]{open2015estimating, camerer2018evaluating}.
While we agree with the importance of direct replications, our study (and similar crowd-sourced analyses before us) suggest that replicating more is simply not enough.
There is only limited value in learning that a particular procedure is replicable if the idiosyncratic nature of the procedure itself might not yield a representative result relative to all possible procedures that could have been applied to the research question.
Beyond a replication crisis, the quantitative sciences are in an inference crisis \citep{rotello2015more, starns2019assessing}.
Well-trained and experienced speech researchers not only applied completely different approaches to the same research question, peer ratings also suggest that they considered most of these alternative approaches acceptable.
Being aware of this idiosyncratic variation between analysts should lead to more nuanced claims and what Breznau et al.~refers to as ``epistemic humility''.

A desired outcome of knowing that different but reasonable measurement choices or statistical approaches might lead to different interpretations of research data is to calibrate our (un)certainty in the strength of the collected evidence and, in turn, communicate that (un)certainty appropriately.
The fact that the choice of measurement, measurement window, and predictor choice affect the answer to the research question further suggests that research assumptions and hypotheses should be formulated in much greater detail, particularly so in regards to how measurement systems (here, the acoustic signal) and underlying conceptual constructs (here, the phonetic expression of typicality) relate to each other.
We should ideally specify the link between conceptual construct and quantitative system---the ``derivation chain'' \citep{dubin1970theory, meehl1990summaries}---prior to data collection and analysis, including defining constructs and their relationship within the quantitative system, specifying auxiliary assumptions and boundary conditions, and defining target measurements, statistical expectations and possible (and impossible) effect magnitudes.
Without well defined derivation chains, we ``are not even wrong'' \citep{scheel2022most} because falsified expectations cannot tell us much about the conceptual constructs they are based on when the relationship between the two is underspecified.

In light of the observed analytic flexibility, what can we do to appropriately calibrate our confidence in our claims?
First of all, through sharing of materials, data and statistical protocols, we can make our idiosyncratic choices transparent to others \citep{munafo2017manifesto, vazire2017quality}.
It further enables the evaluation and verification of underlying claims and allows for the evaluation of empirical, computational and statistical reproducibility \citep{lebel2018unified}.
It allows for alternative analyses to establish analytic robustness \citep{steegen2016increasing} and strengthens attempts to synthesize evidence via meta-analyses \citep[e.g.,][]{nicenboim2018using}
Given that minor procedural changes can sometimes drastically affect the final interpretation of the results \citep{breznau2021observing}, we should ideally share a detailed documentation of the data collection procedure, the measurement choices, the data extraction, and statistical analyses.
Within fields that deal with speech data, open source software that allows to extract acoustic parameters via reproducible scripts can help other researchers to trace back seemingly inconsequential choices during the measurement process \citep[e.g., Praat:][EMU: \citet{winkelmann2017emu}]{boersma2021praat}.

@@

Third, if researchers have a good understanding of relevant analytic degrees of freedom, they could apply all conceivable analytic strategies and compare the results across all combinations of these choices.
This approach is called ``multiverse analysis'' \citep[e.g,][]{steegen2016increasing, harder2020multiverse} and has recently gained popularity across disciplines.

Finally, neither crowd-sourcing nor multiverse analyses will guarantee that all relevant pathways are explored.
Crowd-sourcing is limited by the sampled analysts and their biases.
Multiverse analysis is limited even further by the one group of researchers who define possible analytic pathways.
Eventually, a mature scientific discipline needs to develop a set of detailed quantitative hypotheses of how conceptual constructs manifest themselves in the measured system, i.e.~in the present case how communicative pressures of functions are expressed in the acoustic signal.
This can be achieved by mathematically formalizing verbal expectations or using computational models \citep[e.g.,][]{van2020formalizing, guest2021computational, scheel2021hypothesis, devezer2021case}.

@@

Our study has several limitations that need to be considered when evaluating our results.
First, there is potential for bias.
The coordinating authors have engaged with metascientific research before and have been actively involved in methodological debates about scientific practices including transparency and statistical methods.
We have in the past used the lack of standardized analytical approaches as an argument for proposing behavior and policy changes in the field.
This might have biased our own judgment during the analysis which itself came with many researcher degrees of freedom.
We hope we were able to make these degrees of freedom as well as the timing and reasoning of our analytical choices at least detectable.
However, our results should be independently re-analysed and replicated using a different research question.
Moreover, our sample is an opportunity sample.
We have advertised the project through online platforms which might have led to the exclusion of certain potential researcher groups.
While the number of participating teams is larger than most earlier crowdsourcing projects, it is likely to be too small to estimate for example the impact of certain predictors reliably.
Since predictor levels were not systematically distributed across teams, our estimates are characterized by large uncertainty.
This uncertainty is possibly further inflated by the fact that he research question presented to the teams was vague: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
Interpreting the research question/hypothesis differently in terms of its statistical consequences has recently been shown to explain some variation between analysis teams in many-analysis projects \citep{auspurg2021has}.
However, we consider this very underspecification of research hypotheses in the field of speech science (and beyond, see \citet{scheel2022most}) a common phenomenon.
For example, researchers seem to have not yet agreed on how to acoustically measure cross linguistically common phenomena such as word stress \citep[e.g.][]{gordon2017acoustic}.

\begin{itemize}
\tightlist
\item
  We have not investigated researcher positionality, which is known to be an important factor.
\end{itemize}

Despite these all of these possible sources of bias and uncertainty, our study suggest that at a minimum we can expect the between-team and between-analysis variability that we have observed, which is quite substantial and possibly amplifying biases.

Second, the generalizability of our findings to other disciplines on the one hand and specifically other sub-disciplines of the language sciences is, of course, limited.
We focused on quantitative analyses that require operationalization of a multidimensional signal.
While some of our results can be informative for other disciplines that worke with speech or video signals, they might not be very informative for expected variation between analysts working in qualitative research fields.
This is an important point to make because the cognitive sciences in general, and the language sciences in particular have many research areas that are explored with qualitative methods.
It is conceivable that the discussed issues apply differently or not at all to qualitative data analysis.
